Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-05-06 ms.tex
more changes for casey

\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/cornertest.pdf} 
	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$. The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass. The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$. See text for a complete description. } \label{fig: probability corner} 
\end{figure}

@@

@@

@@

@@

Primarily, we are interested in the intrinsic scatter of the richness-mass relationship. This is because HETDEX is uniquely situated to estimate the scatter, whereas studies rely on stacked data \citeeg{Farahi2016,Simet2016} lose that information. However, for technical reasons we begin by estimating how well HETDEX will constrain the absolute mass scale (something stacked studies excel at). As part of our fitting process to constrain the mass scale, we estimate the overall scatter in the relationship, so it makes sense to begin here.

@@

We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because there are very few clusters with $\lambda>130$ and to better coincide with other observational studies \citeeg{Saro2015}. For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
\begin{equation}
	\mathrm{Log}\ M_{200c}/\Msol = 12.54\pm0.02 + 0.97\pm0.02\ \mathrm{Log}\ \lambda
\end{equation} 
and the Survey observations as
\begin{equation}
	\mathrm{Log}\ M_{200c}/\Msol = 12.78\pm0.04 + 0.86\pm0.03\ \mathrm{Log}\ \lambda
\end{equation} 
This gives $M_{200c} = (1.22\pm...)\times10^{14}$ \Msol and $M_{200c} = (1.44\pm...)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively. In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work \cite{Li2016, Simet2016}. If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.8\pm...)\times10^{14}$ \Msol\ and $M_{200c} = (1.78\pm...)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.

@@

>>>>

\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$. The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass. The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$. See text for a complete description. } \label{fig: probability corner} 
\end{figure*}

@@

		&& \multic{8}{Perfect Observations} \\

@@

		&& \multic{8}{Targeted Observations} \\

@@

		&& \multic{8}{Survey Observations} \\

@@

Primarily, we are interested in the intrinsic scatter of the richness-mass relationship. This is because HETDEX is uniquely situated to estimate the scatter, whereas studies relying on stacked data \citeeg{Farahi2016,Simet2016} lose that information. However, for technical reasons, we begin by estimating how well HETDEX will constrain the absolute mass scale (something stacked studies excel at). As part of our fitting process to constrain the mass scale, we estimate the overall scatter in the relationship, so it makes sense to begin here.

@@

We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because there are very few clusters with $\lambda>130$ and to better coincide with other observational studies \citeeg{Saro2015} which have lower limits on $\lambda$. For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
\begin{equation}
	\mathrm{Log}\ M_{200c}/\Msol = 12.54\pm0.02 + 0.97\pm0.02\ \mathrm{Log}\ \lambda
\end{equation} 
and the Survey observations as
\begin{equation}
	\mathrm{Log}\ M_{200c}/\Msol = 12.78\pm0.04 + 0.86\pm0.03\ \mathrm{Log}\ \lambda
\end{equation} 
This gives $M_{200c} = (1.22\pm...)\times10^{14}$ \Msol and $M_{200c} = (1.44\pm...)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively. In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work \cite{Li2016, Simet2016}. If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.8\pm...)\times10^{14}$ \Msol\ and $M_{200c} = (1.78\pm...)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.

@@

For
